Composable Generalized Consensus

### 2016-01-07 paper/abstract4.tex
Work on the abstract.

To lower this cost, we present a framework for building SMR algorithms out of independent and reusable SMR modules. A module is an SMR
algorithm that can abort and pass the baton to another module, allowing to dynamically switch between modules. 
We propose Composable
Generalized Consensus (CGC), a correctness condition for individual modules, and
we prove that the composition of correct modules is a correct SMR algorithm.
Our framework consists of TLA$^+$ specifications of CGC and of two abstract
types of correct modules, fast rounds and conservative rounds, each providing a template to devise new SMR modules with the help of the TLA$^+$
tools. We show that several well-known SMR algorithms can be modified to
implement fast or conservative rounds, therefore enabling
their composition to obtain a single versatile SMR algorithm.

>>>>

To lower this cost, we present a framework for building SMR algorithms out of
independent and reusable SMR modules. A module is an SMR algorithm that can
abort and pass the baton to another module, allowing to dynamically switch
between modules. Our composition theorem ensures that the composition of any
number of modules satisfying Composable Generalized Consensus (CGC), our
correctness condition for modules, is a correct SMR algorithm.

To help design new modules in practice, we propose TLA$^+$ specifications
of CGC and of two abstract types of modules, fast rounds and conservative
rounds, each providing a template to devise new SMR modules with the help of the
TLA$^+$ tools. We show that several well-known SMR algorithms can be modified to
implement fast or conservative rounds, therefore enabling their composition to
obtain a single versatile SMR algorithm.
